---
title: "The world's anxiety of cybercrime in 2019"
author: "Julie Nguyen"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format:
  pdf:
    documentclass: article
    papersize: a4
    geometry: margin = 1in
    mainfont: "Garamond"
    sansfont: "Garamond"
thanks: 'Code and data are available at: https://github.com/julieenguyennn/World-Risk-Analysis'
abstract: " The emergence of the internet has altered the way we live, work, and communicate with each other. Despite being a tool to improve life in overall, technology and the internet also pose some potential risks that greatly affect the life of people. This paper aims at identifying the perceptions of risk of using the internet among people around the world by exploring the patterns and the relationship between gender, the number of children, the living location and the pereception of risk towards online bullying. Findings show that females tend to be more worried about experiencing cybercrime than males, people having more children also witness the same pattern. Results also show that gender, the number of children, and the living location affect the anxiety of the prospect of being a victim of cybercrime."
number-sections: true
bibliography: reference.bib
execute: 
  message: false
  warning: false
  echo: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(janitor)
library(tidyverse)
library(knitr)
library(RColorBrewer)
library(kableExtra)
library(ggplot2)
library(cowplot)

internet_risk <- read.csv(here::here("inputs/cleaned_data.csv"))

# Format data
internet_risk$gender <- as.factor(internet_risk$gender)
internet_risk$online_bullying <- as.factor(internet_risk$online_bullying)
cleaned_data$education <- as.factor(cleaned_data$education)
cleaned_data$urbanicity <- as.factor(cleaned_data$urbanicity)
cleaned_data$children_in_household <- as.factor(cleaned_data$children_in_household)
internet_risk$false_info <- as.factor(internet_risk$false_info)
internet_risk$fraud <- as.factor(internet_risk$fraud)
```

# Introduction

The emergence of the internet has altered the way we live, work, and
communicate with each other. It has become an integral part of our daily
lives, offering numerous benefits such as instant access to information,
online shopping, and communication with people from all over the world.
However, along with these benefits, the Internet also poses various
risks to its users.

The dangers of using the internet increase as it develops and expands.
Some of the main dangers that people encounter include cybercrime,
online scams, identity theft, cyberbullying, and pestering. Regardless
of the person's age, gender, or location, these dangers can have
significant financial and mental repercussions. Findings from
@globalrisk about emerging technology and its potential risk suggest
that the Internet of Things (IoT) fell into the group of technology that
had lots of risks, but not so much reward. On the one hand, they gave
more access to the life of people. On the other hand, they could also
"give cyber-criminals a window to our world".

Therefore, it is essential to recognize these dangers. Understanding and
identifying risk is as important as keeping the world healthy. This
paper focuses on identifying the perceptions of risk of using the
internet among people around the world. The paper also analyzes the
correlation between education, income, and living locations, and how
these factors affect the perception of risk towards the internet. In
exploring the patterns of risk perception, the paper hopes to provide
insights into people in different demographics experience and perceive
potential risks posed by digital technology, through which will improve
digital well-being, raise awareness, and enhance the ways to protect
internet users in the world.

This paper will firstly explore the patterns of risk posed by technology
in the world and in different global regions from the data of @riskpoll
in 2019 using @rpackage. Various groups (of gender, education, and
income) are observed to see how they affect the respondent's perception
of risk caused by the internet. Other packages such as tidyverse
[@tidyverse], readr [@readr], haven [@haven], janitor [@janitor],
ggplot2 [@ggplot], tidymodels [@tidymodels] etc. are also used to
aggregate, visualize, and model the data.

The main findings show that females tend to experience more anxiety
towards the prospect of cybercrime than males. People living in
low-income countries tend to witness the same pattern. People who have
less kids tend to be less worried about the potential of risk.

In the following paper, I will delve into the data from @riskpoll, and
how it is obtained and arranged for proper analysis. This section will
also guide us through the understanding of the initial survey and
ethical concerns regarding the data collection. Moving on to the Model
section, we will discuss our model and its implications for how we
interpret our results going forward. In the Results section, graphical
data is shown as to provide a clear understanding of the results given.
Lastly, the Discussion section will include what has been done, what was
learnt as well as identify some weaknesses and propose the next steps
for the paper.

# Data

## Dataset

To attempt an analysis on ...., I manipulated the @riskpoll data from
the year 2019. These data are collected by the Llyod's... The dataset
was gatherd in... and last updated on... The raw data includes
observations. Using R [@rpackage], tidyverse [@tidyverse], readr
[@readr], haven [@haven], janitor [@janitor], ggplot2 [@ggplot],
tidymodels [@tidymodels], I cleaned and extracted the necessary data to
complete an exploratory analysis and modelling.

## Variables

## Ethical Concerns

# Model

Multiple logistic regression is used for analyzing the correlation
between gender, the number of children, living location and the anxiety
of the prospect of being a victim of cybercrime.

```{r}
xtabs(~ online_bullying + gender, data = internet_risk)
xtabs(~ online_bullying + children_in_household, data = internet_risk)
xtabs(~ false_info + gender, data = internet_risk)
xtabs(~ false_info + education, data = internet_risk)
xtabs(~ fraud + education, data = internet_risk)
```

```{r}
data_bullying <- internet_risk %>% select(online_bullying,gender,education,urbanicity,children_in_household)

log_gender_bullying <- glm(online_bullying ~ gender, data=data_bullying, family="binomial")
summary(log_online_bullying)

predicted_data <- data.frame(probability_of_online_bullying = log_gender_bullying$fitted.values, gender=data_bullying$gender)

ggplot(data = predicted_data, aes(x = gender, y = probability_of_online_bullying)) +
  geom_point(aes(color = gender), size = 5) +
  xlab("Gender") +
  ylab("Predicted probability of getting online bullying")

xtabs(~ probability_of_online_bullying + gender, data = predicted_data)
```

```{r}
log_children <- glm(online_bullying ~ children_in_household, data=internet_risk, family="binomial")
summary(log_children)
```

```{r}
children_risk <- internet_risk %>%
  filter(l27a == "1" | l27a == "2") %>% 
  select(children_in_household, l27a) %>%
  rename("anxiety" = l27a)

children_risk <- children_risk %>%
  mutate(children_in_household = case_when(
    children_in_household == "0" ~ "None",
    children_in_household == "1" ~ "1",
    children_in_household == "2" ~ "2",
    children_in_household == "3" ~ "3",
    children_in_household == "4" ~ "4",
    children_in_household == "5" ~ "5+"
    ), children_in_household = factor(children_in_household, levels = c(
      "None", "1", "2", "3", "4", "5+"
    )),
    anxiety = case_when(anxiety == "2" ~ "0", anxiety == "1" ~ "1"))

children_risk$anxiety <- as.numeric(children_risk$anxiety)

# Apply logistic model
children_bully_model <-
  glm(
    anxiety ~ children_in_household,
    data = children_risk,
    family = "binomial"
  )

summary(children_bully_model)
```

```{r}

```

# Results

```{r}

```

# Discussion

This gives valuable insights for pre-covid.

# Appendix

# References
