---
title: "The world's anxiety of cybercrime in 2019"
author: "Julie Nguyen"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format:
  pdf:
    documentclass: article
    papersize: a4
    geometry: margin = 1in
    mainfont: "Garamond"
    sansfont: "Garamond"
thanks: 'Code and data are available at: https://github.com/julieenguyennn/World-Risk-Analysis'
abstract: " The emergence of the internet has altered the way we live, work, and communicate with each other. Despite being a tool to improve life in overall, technology and the internet also pose some potential risks that greatly affect the life of people. This paper aims at identifying the perceptions of risk of using the internet among people around the world by exploring the patterns and the relationship between gender, the number of children, the living location and the pereception of risk towards online bullying. Findings show that females tend to be more worried about experiencing cybercrime than males, people having more children also witness the same pattern. Results also show that gender, the number of children, and the living location affect the anxiety of the prospect of being a victim of cybercrime."
number-sections: true
bibliography: reference.bib
execute: 
  message: false
  warning: false
  echo: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(janitor)
library(tidyverse)
library(knitr)
library(RColorBrewer)
library(kableExtra)
library(ggplot2)
library(ggpubr)
library(gridExtra)

internet_risk <- read.csv(here::here("inputs/cleaned_data.csv"))

# Format data
internet_risk$gender <- as.factor(internet_risk$gender)
internet_risk$online_bullying <- as.factor(internet_risk$online_bullying)
internet_risk$education <- as.factor(internet_risk$education)
internet_risk$urbanicity <- as.factor(internet_risk$urbanicity)
internet_risk$children_in_household <- as.factor(internet_risk$children_in_household)
internet_risk$false_info <- as.factor(internet_risk$false_info)
internet_risk$fraud <- as.factor(internet_risk$fraud)
```

# Introduction

The emergence of the internet has altered the way we live, work, and
communicate with each other. It has become an integral part of our daily
lives, offering numerous benefits such as instant access to information,
online shopping, and communication with people from all over the world.
However, along with these benefits, the Internet also poses various
risks to its users.

The dangers of using the internet increase as it develops and expands.
Some of the main dangers that people encounter include cybercrime,
online scams, identity theft, cyberbullying, and pestering. Regardless
of the person's age, gender, or location, these dangers can have
significant financial and mental repercussions. Findings from
@globalrisk about emerging technology and its potential risk suggest
that the Internet of Things (IoT) fell into the group of technology that
had lots of risks, but not so much reward. On the one hand, they gave
more access to the life of people. On the other hand, they could also
"give cyber-criminals a window to our world".

Therefore, it is essential to recognize these dangers. Understanding and
identifying risk is as important as keeping the world healthy. This
paper focuses on identifying the perceptions of risk of using the
internet among people around the world. The paper also analyzes the
correlation between education, income, and living locations, and how
these factors affect the perception of risk towards the internet. In
exploring the patterns of risk perception, the paper hopes to provide
insights into people in different demographics experience and perceive
potential risks posed by digital technology, through which will improve
digital well-being, raise awareness, and enhance the ways to protect
internet users in the world.

This paper will firstly explore the patterns of risk posed by technology
in the world and in different global regions from the data of @riskpoll
in 2019 using @rpackage. Various groups (of gender, education, and
income) are observed to see how they affect the respondent's perception
of risk caused by the internet. Other packages such as tidyverse
[@tidyverse], readr [@readr], haven [@haven], janitor [@janitor],
ggplot2 [@ggplot], tidymodels [@tidymodels] etc. are also used to
aggregate, visualize, and model the data.

The main findings show that females tend to experience more anxiety
towards the prospect of cybercrime than males. People living in
low-income countries tend to witness the same pattern. People who have
less kids tend to be less worried about the potential of risk.

In the following paper, I will delve into the data from @riskpoll, and
how it is obtained and arranged for proper analysis. This section will
also guide us through the understanding of the initial survey and
ethical concerns regarding the data collection. Moving on to the Model
section, we will discuss our model and its implications for how we
interpret our results going forward. In the Results section, graphical
data is shown as to provide a clear understanding of the results given.
Lastly, the Discussion section will include what has been done, what was
learnt as well as identify some weaknesses and propose the next steps
for the paper.

# Data

## Dataset

To attempt an analysis on ...., I manipulated the @riskpoll data from
the year 2019. These data are collected by the Llyod's... The dataset
was gatherd in... and last updated on... The raw data includes
observations. Using R [@rpackage], tidyverse [@tidyverse], readr
[@readr], haven [@haven], janitor [@janitor], ggplot2 [@ggplot],
tidymodels [@tidymodels], I cleaned and extracted the necessary data to
complete an exploratory analysis and modelling.

## Variables

09 variables were selected to conduct analysis for the paper including
06 variables for respondents' general information (gender, education
attainment, global region, urbanicity, and the number of children in
household) and 03 variables relating to the anxiety towards the risk of
being online (cyber bullying, false information and fraudulent
activities). I first viewed the presence of anxiety towards different
gender, education, and global region to investigate the global trend of
online risk and anxiety in the year 2019. Along with these variables,
the remainings are used later on to explore whether there is a causal
relationship between the respondent's identity and their being worried
about risks posed by the internet.

The anxiety towards different types of cybercrime were measure by asking
the respondents "When using the Internet or social media, do you worry
about any of the following things happening to you?". The answered is
scaled as "Yes", "No". Gender of the respondents was recorded as 1 for
"Male", and 2 for "Female". For the variable regarding the number of
children in household, it is categorized into from 0 to 5 as the number
of children accordingly, except for 5 was coded as "5 and above".
Urbanicity refers to the place that the respondents were living in at
the time of the survey. It is recorded as 1 for "A rural area or on a
farm/Small town or village", and 2 for "A large city/Suburb of a large
city". Lastly, the education attainment of the respondent is divided
into 3 levels "Up to 8 years of basic education", "9-15 years of
education", and "Completed four years of education beyond high school
and/or received a 4-year college degree". Other types of responses that
fell into "Do not Know" and "Refused" in all questions are omitted from
analysis.

## Plot

```{r, include = FALSE}
# Global internet use by region
global_internet <- internet_risk %>% select(global_region, internet_use)

global_internet <- global_internet %>% group_by(global_region) %>% 
  count(internet_use)

global_internet <- global_internet %>% ggplot(aes(x = global_region, y = n), fill = global_region) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = 'none',
        text = element_text(size = 8)) +
  scale_fill_brewer() +
  labs(x = "Global Region",
       y = "Internet Use",
       title = "Total internet use globally by region")

# Risk of cyberbullying by region
risk_by_region <- internet_risk %>% select(global_region,online_bullying,false_info,fraud)

bully_region <- risk_by_region %>%
  ggplot(aes(x = global_region, fill = online_bullying)) +
  geom_bar(position = "fill") +
  scale_fill_discrete(name = "Presence of Anxiety") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        text = element_text(size = 8)) +
  labs(x = "Global Region",
       y = "Percentage of anxiety towards online bullying")

# Risk of false information by region
false_info_region <- risk_by_region %>%
  ggplot(aes(x = global_region, fill = false_info)) +
  geom_bar(position = "fill") +
  scale_fill_discrete(name = "Presence of Anxiety") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        text = element_text(size = 8)) +
  labs(x = "Global Region",
       y = "Percentage of anxiety towards false information")

# Risk of frauds by region
fraud_region <- risk_by_region %>%
  ggplot(aes(x = global_region, fill = fraud)) +
  geom_bar(position = "fill") +
  scale_fill_discrete(name = "Presence of Anxiety") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        text = element_text(size = 8)) +
  labs(x = "Global Region",
       y = "Percentage of anxiety towards online frauds")

# Global internet use by gender
gender_internet <- internet_risk %>% select(gender, internet_use)

gender_internet <- gender_internet %>% group_by(gender) %>% 
  count(internet_use)

gender_internet <- gender_internet %>% ggplot(aes(x = gender, y = n), fill = gender) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = 'none',
        text = element_text(size = 8)) +
  scale_fill_brewer() +
  labs(x = "Gender",
       y = "Internet Use",
       title = "Total internet use globally by gender")

# Risk of cyberbullying by gender
risk_by_gender <- internet_risk %>% select(gender,online_bullying,false_info,fraud)

bully_gender <- risk_by_gender %>%
  ggplot(aes(x = gender, fill = online_bullying)) +
  geom_bar(position = "fill") +
  scale_fill_discrete(name = "Presence of Anxiety") +
  labs(x = "Gender",
       y = "Percentage of anxiety towards online bullying",
       title = "Anxiety towards online bullying by region")

# Risk of false information by region
false_info_gender <- risk_by_gender %>%
  ggplot(aes(x = gender, fill = false_info)) +
  geom_bar(position = "fill") +
  scale_fill_discrete(name = "Presence of Anxiety") +
  labs(x = "Gender",
       y = "Percentage of anxiety towards false information",
       title = "Anxiety towards false information by region")

# Risk of frauds by region
fraud_gender <- risk_by_gender %>%
  ggplot(aes(x = gender, fill = fraud)) +
  geom_bar(position = "fill") +
  scale_fill_discrete(name = "Presence of Anxiety") +
  labs(x = "Gender",
       y = "Percentage of anxiety towards online frauds",
       title = "Anxiety towards online frauds by region")
```

```{r internetuse, fig.height=3, fig.cap="Anxiety towards cyber risks by region", fig.pos="H", echo=FALSE, warning=FALSE, message = FALSE}
sumgraphs <-
  grid.arrange(global_internet, gender_internet,
               ncol = 2)
```

@internetuse depicts the demographics of total internet use globally by
region and gender. A total number of 86,088 observations is recorded as
having used the internet in the last 30 days from the time of survey.
Among 86,088 observations, it is recorded the the majority comes from
Europe, with 15.47% in Northern/Western Europe, 11.23% in Southern
Europe, and 8.21% in Eastern Europe. On the other hand, the region of
Australia and New Zealand only witnesses a total of 1666 respondents,
which takes up 1.94% of the total observations. Regarding the gender,
the survey witnesses a quite equal proportion of female and male
respondents, 50.75% and 49.25% respectively.

```{r fig.height=3, fig.cap="Anxiety towards cyber risks by region", fig.pos = "H", echo=FALSE, warning=FALSE, message = FALSE}
#| fig-lab: fig-regionrisk
ggarrange(bully_region, false_info_region, fraud_region, ncol=3, common.legend = TRUE, legend="bottom")
```

@fig-regionrisk illustrates the proportion of respondents feeling
anxious towards the three types of cybercrime. In general, people were
more worried about the prospect of being a victim of false information.
A majority of respondents in Africa reported to have been worried about
being online bullied, with a percentage of xxx% in Central/Western
Africa, xxx% in Eastern Africa, xxx% in North Africa, and xxx% in
Southern Africa. People from Australia and New Zealand were deeply
concerned with confronting false information and fraudulent activities
online. On the other hand, the region of Central Asia and South Asia
recorded similar attitudes of being "not worried" than "worried" for any
of the three types of cybercrime.

```{r fig.height=3, fig.cap="Anxiety towards cyber risks by gender", fig.pos = "H", echo=FALSE, warning=FALSE, message = FALSE}
#|fig-lab: fig-genderrisk
ggarrange(bully_gender, false_info_gender, fraud_gender, ncol=3, common.legend = TRUE, legend="bottom")
```

@fig-genderrisk shows the percentage of people feeling worried about
three types of cybercrime by gender. There is an overall trend, although
not too distinct, that female respondents feel more anxious than male
towards the online risks. It is also obvious that both male and female respondents felt more anxious towards the prospect of facing false information when using the internet and social media.

# Model

Multiple logistic regression is used for analyzing the correlation
between gender, the number of children, living location and the anxiety
of the prospect of being a victim of cybercrime.
logit(p) = β0 + β1\*x1 + β2\*x2 + \... + βn\*xn

```{r}
xtabs(~ online_bullying + gender, data = internet_risk)
xtabs(~ online_bullying + children_in_household, data = internet_risk)
xtabs(~ false_info + gender, data = internet_risk)
xtabs(~ false_info + education, data = internet_risk)
xtabs(~ fraud + education, data = internet_risk)
```

```{r}
data_bullying <- internet_risk %>% select(online_bullying,gender,education,urbanicity,children_in_household)

log_gender_bullying <- glm(online_bullying ~ gender, data=data_bullying, family="binomial")
summary(log_gender_bullying)

predicted_data <- data.frame(probability_of_online_bullying = log_gender_bullying$fitted.values, gender=data_bullying$gender)

ggplot(data = predicted_data, aes(x = gender, y = probability_of_online_bullying)) +
  geom_point(aes(color = gender), size = 5) +
  xlab("Gender") +
  ylab("Predicted probability of getting online bullying")

xtabs(~ probability_of_online_bullying + gender, data = predicted_data)
```

```{r}
log_children <- glm(online_bullying ~ children_in_household, data=internet_risk, family="binomial")
summary(log_children)
```

```{r}

```

```{r}

```

# Results

```{r}

```

# Discussion

This gives valuable insights for pre-covid.

# Appendix

# References
